Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-09-18 Ben_Manuscripts/structure_paper/Draft.tex
Converted figures to .pdf

  \begin{table}[h]
  \centering
  \begin{tabular}{c|ccccc}
  \toprule
 		     & \multicolumn{5}{c}{Normalized Reflection Intensity}                   \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.0        &  1.0       &  1.0      &  1.0       &  1.0               \\
  R-pores    & 4.91       & 49.5       & 54.0      & 50.8       & 53.4               \\
  R-spots    & 1.2        &  1.2       &  1.2      &  1.1       &  1.1               \\
  R-$\pi$    & 2.8        & 44.0       &  7.7      &  8.4       & 10.1               \\
  R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
  \hline
   		     & \multicolumn{5}{c}{Reflection Location ($|\mathbf{q}|~\AA^{-1}$)}     \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.39       &  1.44      &  1.44     & 1.42       & 1.43               \\  
  R-pores    & 0.176      &  0.170     &  0.170    & 0.173      & 0.172              \\
  R-spots    & 1.39       &  1.44      &  1.44     & 1.42       & 1.43               \\
  R-$\pi$    & 1.70       &  1.41      &  1.42     & 1.40       & 1.40               \\
  R-double   & 0.85       &  --        & --        &  --        & --                 \\ 
  \bottomrule
  \end{tabular}
  \caption{The simulated XRD patterns of the systems tested, normalized so that
	  the average intensity of R-alkanes in each pattern equals 1, show R-pores and
	  R-$\pi$ reflections that are significantly higher than experiment and R-spots
	  reflections that are slightly lower than experiment. R-double does not appear
	  in any simulated patterns, and thus has no measurable intensity. In terms of 
	  the locations of the reflections, R-pores, R-alkanes and R-spots appear at $q$
	  values that close to experiemnt, while R-$\pi$ appears at a significantly lower
	  $q$ value than experiment.}
  \label{table:relative_intensities_300K} 
  \end{table}

@@

  \begin{figure}[!htb]
  \begin{subfigure}{0.32\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rzplot_layered_280K_jet.png}
  	\caption{}\label{fig:sandwiched280K}
  \end{subfigure}
  \begin{subfigure}{0.32\linewidth}
    \includegraphics[width=\textwidth]{tilt_dist.png}
    \caption{}\label{fig:tilt}
  \end{subfigure}
  \begin{subfigure}{0.32\linewidth}
	\centering
	\includegraphics[width=\textwidth]{tails_rzplot_jet.png}
	\caption{}\label{fig:tails_rzplot}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\linewidth}
    \centering
	\includegraphics[scale=0.2]{centroids.png}
  \caption{}\label{fig:centroids}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\linewidth}
        \centering
	        \includegraphics[width=\linewidth]{hexagonal_tail_packing.png}
	        \caption{}~\label{fig:layered_tails}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\textwidth}
        	\centering
	        \includegraphics[width=\linewidth]{hexagonal_ft.png}  % generated from hexagonal_packing.py
	        \caption{}~\label{fig:hexagonal_ft}
  \end{subfigure}
  \caption{(a) R-spots increases in intensity when the temperature of the system is 
      lowered to 280K. (b) We measured the average angle made between each monomer 
      alkane tail and the membrane plane. The average tilt angle (dashed line) is 
      near -2\degree~which is far from the 37\degree~tilt angle previously used to
      explain R-spots. (c) To isolate the main cause of R-spots, we removed all atoms
      from the trajectory except for carbon atoms that constitute the tails. The
      simulated XRD pattern of the tails-only trajectory still shows R-spots. (d)
      Since the tails stay relatively flat, we plotted the center of mass of the first
      four carbon atoms of each tail originating from the head groups (for example,
      green colored centroids in the plot surround the red centroid in hexagonal fashion).
      Visually, the packing looks hexagonal. (e) We hypothesize
      that R-spots is the result of ordered tail packing. Defining
      the membrane plane to be 0\degree, we measured the angles between each center of 
      mass and its nearest neighbor center of masses for the equilibrated 
      sandwiched configuration simulated at 280K. Peaks appear in the distribution at 
      $-60\degree$, $0\degree$ and $60\degree$. (f) The Fourier transform of a hexagonally
      packed grid of points defined by the angles in (e) shows intensity at the same
      locations where we expect to see R-spots, as well as intensity along the $q_z$ axis
      where R-$\pi$ would appear.}~\label{fig:tail_packing}
  \end{figure}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{exp_rsection_fit.pdf}
  \caption{FWHM = 0.792 $\pm$ 0.009 $\AA^{-1}$}\label{fig:exp_rsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sim_rsection_fit.png}
  \caption{FWHM = 0.796 $\pm$ 0.011 $\AA^{-1}$}\label{fig:sim_rsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{exp_zsection_fit.pdf}
  \caption{FWHM = 0.110 $\pm$ 0.003 $\AA^{-1}$}\label{fig:exp_zsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sim_zsection_fit.png}
  \caption{FWHM = 0.163 $\pm$ 0.011 $\AA^{-1}$}\label{fig:sim_zsection_fit}
  \end{subfigure}
  \caption{
  The maximum intensity of R-$\pi$ generated from simulations of the ordered
  parallel displaced configuration is 3 times larger than experiment. The $q_r$
  cross-section of R-$\pi$ ((a) and (b)) is qualitatively different between 
  experiment (a) and simulation (b). We fit Lorentzian profiles to each peak and
  the FWHM (full width at half maximum) of the simulated pattern agrees with experiment within error. However
  the fit to the simulated data is affected by the three sharp peaks which appear
  near $q_r$ = 0. The $q_z$ cross-sections of R-$\pi$ ((c) and (d)) are 
  qualitatively similar. Each fits a Lorentzian profile well, however the FWHM
  of the simulated cross-section (d) is 48\% larger than the experimental 
  cross-section. Additionally, the peak of the simulated $q_z$ cross-section is 
  located at a lower $q_z$ value than experiment.}\label{fig:rpi_exp_comparison}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_sandwich.png}
  \caption{Sandwiched, Ordered Basin}\label{fig:z_correlation_sandwich}
  \end{subfigure}  
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_offset.png}
  \caption{Parallel Displaced, Ordered Basin}\label{fig:z_correlation_offset}
  \end{subfigure}  
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_sandwich_disordered.png}
  \caption{Sandwiched, Disordered Basin}\label{fig:z_correlation_sandwich_disordered}
  \end{subfigure}  
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_offset_disordered.png}
  \caption{Parallel Displaced, Disordered Basin}\label{fig:z_correlation_offset_disordered}
  \end{subfigure}  
  %MRS10: should say something here about whether this is consistent or not with experiement (and why/why not)
  %MRS10: maybe include correlation lengths as well calculated from these, and compare to experiment?  I know it's in the table as well, but seems missing here.  1D correlation functions are given, but not how that data proves central points.
  \caption{1D correlation functions of the center of masses of aromatic head
	  groups, $g(z)$, show decaying oscillatory behavior and have consistent correlation lengths with experiment. We calculated the
	  correlation length by fitting a decaying exponential function
	  (Equation~\ref{eqn:decaying_exponential}) to the peaks of $g(z)$. The
	  correlation length is longer for ordered basin systems
	  (Table~\ref{table:correlation_length}). We did not attempt to calculate the
	  correlation length for (d) because there are no clear peaks. We assume that its
	  correlation length is less than the vertical distance between monomers.}\label{fig:correlation}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{intensity_vs_zsigma.png}
  \caption{}\label{fig:intensity_vs_zsigma}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{rpi_xsection_vs_zsigma.png}
  \caption{}\label{fig:rpi_xsection_vs_zsigma}
  \end{subfigure}
  \caption{We can decrease the maximum intensity of R-$\pi$ by increasing
  thermal noise in the $z$-direction, however the $q_r$ cross-section profile does
  not change. (a) The intensity of R-$\pi$ drops precipitously as we increase
  $\sigma_z$. We can decrease the intensity of R-$\pi$, relative to the
  background intensity, relative to systems with simulation levels of disorder (blue)
  %as seen in simulation (blue) 
  by a factor of 3 when we
  increase $\sigma_z$ by 12\% (green) and by a factor of 15 when we increase
  $\sigma_z$ by 27\% (red). (b) Although the maximum intensity of R-$\pi$
  decreases with increasing $\sigma_z$, the peak shape remains the same.}\label{fig:znoise}
  \end{figure}

  However, when we allow monomer columns to move independently in the
  $z$-direction, the intensity of R-$\pi$ drops and the $q_r$ cross-section of
  the simulated diffraction patterns smooths out. We can demostrate this by
  creating a simplified sandwiched configuration (simplified in the same way as
  described above), 
  %simple systems 
  %MRS10: simple systems is not very exact. Point scatters that represent the head groups?
  %BJC11: It feels redundant and wordy saying the above rather than simple systems.
  with varying amounts of statistical correlation between columns. In the low
  limit, the COM of columns are situated at the same $z$-coordinate.
  We allow increasing independence of columns by randomly shifting each column in
  the $z$-direction according to a uniform distribution bounded by (0, $f \times
  \mathit{d}_{equil}$) where $f$ ranges between 0 and 1. We limit this discussion
  to the sandwiched configuration since it is not feasible for columns in the
  parallel displaced configuration, as we have set them up, to move past each
  other. When $f = 1$, the columns move independently and the $q_r$ cross-section
  smooths out completely (Figure~\ref{fig:column_displacement}). Any amount of
  dependence results in some presence of independent sharp peaks, though
  significantly attenuated at $f$ nearer 1. The intensity of R-$\pi$ also
  decreases with increasing column independence. We see an 8-fold decrease in the
  intensity of R-$\pi$ when $f=1$ versus when $f=0$ for our simplified model
  systems.
  %MRS12: somewhere will have to talk about stability and relative free energy of the more disordered initial configurations.
  %MRS12: we MIGHT have to look at more disordered initial configurations. I think this can likely be done with just equilibration, where we see how different the quenched disorder when starting from an ensemble of structures, and putting off actually calculating scattring from a large number of simulations. 
  \begin{figure}
  \centering
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_sr0.png}
  \caption{$f$ = 0}\label{fig:sf_qy_sr0}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_sr75.png}
  \caption{$f$ = 0.75}\label{fig:sf_qy_sr75}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_sr100.png}
  \caption{$f$ = 1}\label{fig:sf_qy_sr100}
  \end{subfigure}
  \caption{As we increase column independence using the $f$ parameter, the
	  intensity of R-$\pi$ decreases and the $q_r$ cross-section of the simulated
	  diffraction pattern becomes more smooth.  (a) When we place all columns at the
	  same reference $z$ coordinate, $f$ = 0, the intensity of R-$\pi$ is 18.3 and is
	  characterized by sharp Bragg-like peaks. (b) When columns have a moderate
	  amount of independence, $f$ = 0.75, the intensity of R-$\pi$ decreases 5-fold
	  to 3.7. The edges of the peak are beginning to smooth out, but sharp peaks
	  still exist. (c) When columns are completely independent, $f$ = 1, the
	  intensity of R-$\pi$ decreases 8-fold to 2.3 and the cross-section is
          relatively smooth.}\label{fig:column_displacement}
  \end{figure}

@@

  %BJC9: Note that the magnitude of the correlation function is much lower than 
  % in figure 10a. That's because many of the z-slices are zero when you include
  % all of them.
  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{z_correlation_fullbox.png}
  \caption{When we average all $z$-slices of the 3D correlation function, the 
  correlation length of the ordered sandwich configuration nearly triples.}\label{fig:z_correlation_fullbox}
  \end{figure}

@@

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{qy_fwhm.png}
  \caption{Increasing the amount of disorder in the $xy$ plane decreases the
	  FWHM of the $q_y$ cross-section of R-$\pi$. When we cut the amount of $r$ and
	  $\theta$ disorder in half (Noise factor = 0.5), the FWHM increases by 88\%. When
	  we double the disorder (Noise factor = 2), the FWHM decreases by
	  51\%.}\label{fig:qy_fwhm}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sandwiched_ensemble_rsection.png}
  \caption{Sandwiched}\label{fig:sandwiched_ensemble_rsection}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_rsection.png}
  \caption{Parallel Displaced}\label{fig:offset_ensemble_rsection}
  \end{subfigure}
  \caption{The $q_r$ section of R-$\pi$ is much smoother when we generate simulated XRD
  		   patterns from an ensemble of 40 independent simulations, suggesting that much of the extra initial intensity may be due to the starting conditions. The maximum 
  		   intensity of R-$\pi$ is 3$\times$ higher in the sandwiched configuration (a)
  		   than in the parallel displaced configuration (b).}\label{fig:ensemble_XRD}
  \end{figure}

@@

  %BJC15: will not waste much time formatting until we converge on a figure 
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_pooled.png}
  \caption{Distributions of deviations from ideal positions generated with data
  from all independent simulations}\label{fig:offset_ensemble_pooled}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  % BJC15: Also, do you have a preference for 1-sigma or 95 % confidence intervals? I think the 95 % is fine as is
  %MRS15: 95% is fine.
  \includegraphics[width=\textwidth]{offset_ecdfs.png}
  \caption{Empirical cumulative distribution functions generated from (a) and
  from simulation ensembles.}\label{fig:offset_ecdfs}
  \end{subfigure}
  \caption{(a) The distributions of the head group COM deviations
  from their idealized positions generated using pooled data from all
  frames of each independent configuration are symmetric, implying that 
  there is equal probability for a head group to displace in the positive
  or negative $z$, $r$ or $\theta$-direction. (b) The COM position of a 
  given head group is displaced randomly upon quenching. The ECDF generated from
  the pooled distributions (black) in (a) agree with the means of the 
  ECDFs generated from each COM (red). The red error bars are larger than
  the black error bars since there is a wider distribution of mean COM
  deviations than the mean deviations of distributions sampled from the full
  distribution.}\label{fig:full_ensemble_distributions}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_stds.png}
  \caption{}\label{fig:offset_ensemble_stds}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_means.png}
  \caption{}\label{fig:offset_ensemble_means}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_regional_density.pdf}
  \caption{}\label{fig:offset_ensemble_regional_density}
  \end{subfigure}
  \caption{(a) The standard deviation of the distribution of quenched disorder
  from the first 5 ns of the main ordered parallel displaced system studied in
  this paper (black dashed line) is in agreement with the distribution of quenched disorder 
  standard deviations calculated from the ensemble of simulations (histogram). 
  (b) The mean values of $r$ and $\theta$ from the first 5 ns of the main
  system trajectory (black dashed line) is in agreement with the distribution of mean values
  calculated from each simulation in the ensemble (histogram). The mean values of $z$
  are necessarily 0 so they are not plotted. (c) The radial densities of tail
  atoms, head group atoms and sodium atoms calculated from the first 5 ns of the
  main system simulation trajectory (black lines) and from the ensemble of 
  trajectories (all other lines) look qualitatively similar.}\label{fig:ensemble_stds}
  \end{figure}

>>>>

\begin{table}[h]
  \centering
  \begin{tabular}{c|ccccc}
  \toprule
 		     & \multicolumn{5}{c}{Normalized Reflection Intensity}                   \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.0        &  1.0       &  1.0      &  1.0       &  1.0               \\
  R-pores    & 4.91       & 49.5       & 54.0      & 50.8       & 53.4               \\
  R-spots    & 1.2        &  1.2       &  1.2      &  1.1       &  1.1               \\
  R-$\pi$    & 2.8        & 44.0       &  7.7      &  8.4       & 10.1               \\
  R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
  \hline
   		     & \multicolumn{5}{c}{Reflection Location ($|\mathbf{q}|~\AA^{-1}$)}     \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.39       &  1.44      &  1.44     & 1.42       & 1.43               \\  
  R-pores    & 0.176      &  0.170     &  0.170    & 0.173      & 0.172              \\
  R-spots    & 1.39       &  1.44      &  1.44     & 1.42       & 1.43               \\
  R-$\pi$    & 1.70       &  1.41      &  1.42     & 1.40       & 1.40               \\
  R-double   & 0.85       &  --        & --        &  --        & --                 \\ 
  \bottomrule
  \end{tabular}
    \caption{The simulated XRD patterns of the systems tested, normalized so that
	  the average intensity of R-alkanes in each pattern equals 1, show R-pores and
	  R-$\pi$ reflections that are significantly higher than experiment and R-spots
	  reflections that are slightly lower than experiment. R-double does not appear
	  in any simulated patterns, and thus has no measurable intensity. In terms of 
	  the locations of the reflections, R-pores, R-alkanes and R-spots appear at $q$
	  values that close to experiment, while R-$\pi$ appears at a significantly lower
	  $q$ value than experiment.\label{table:relative_intensities_300K}}
  \end{table}

@@

  \begin{figure}[!htb]
  \begin{subfigure}{0.32\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rzplot_layered_280K_jet.pdf}
  	\caption{}\label{fig:sandwiched280K}
  \end{subfigure}
  \begin{subfigure}{0.32\linewidth}
    \includegraphics[width=\textwidth]{tilt_dist.pdf}
    \caption{}\label{fig:tilt}
  \end{subfigure}
  \begin{subfigure}{0.32\linewidth}
	\centering
	\includegraphics[width=\textwidth]{tails_rzplot_jet.pdf}
	\caption{}\label{fig:tails_rzplot}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\linewidth}
    \centering
	\includegraphics[scale=0.2]{centroids.pdf}
  \caption{}\label{fig:centroids}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\linewidth}
        \centering
	        \includegraphics[width=\linewidth]{hexagonal_tail_packing.pdf}
	        \caption{}~\label{fig:layered_tails}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\textwidth}
        	\centering
	        \includegraphics[width=\linewidth]{hexagonal_ft.pdf}  % generated from hexagonal_packing.py
	        \caption{}~\label{fig:hexagonal_ft}
  \end{subfigure}
  \caption{(a) R-spots increases in intensity when the temperature of the system is 
      lowered to 280K. (b) We measured the average angle made between each monomer 
      alkane tail and the membrane plane. The average tilt angle (dashed line) is 
      near -2\degree~which is far from the 37\degree~tilt angle previously used to
      explain R-spots. (c) To isolate the main cause of R-spots, we removed all atoms
      from the trajectory except for carbon atoms that constitute the tails. The
      simulated XRD pattern of the tails-only trajectory still shows R-spots. (d)
      Since the tails stay relatively flat, we plotted the center of mass of the first
      four carbon atoms of each tail originating from the head groups (for example,
      green colored centroids in the plot surround the red centroid in hexagonal fashion).
      Visually, the packing looks hexagonal. (e) We hypothesize
      that R-spots is the result of ordered tail packing. Defining
      the membrane plane to be 0\degree, we measured the angles between each center of 
      mass and its nearest neighbor center of masses for the equilibrated 
      sandwiched configuration simulated at 280K. Peaks appear in the distribution at 
      $-60\degree$, $0\degree$ and $60\degree$. (f) The Fourier transform of a hexagonally
      packed grid of points defined by the angles in (e) shows intensity at the same
      locations where we expect to see R-spots, as well as intensity along the $q_z$ axis
      where R-$\pi$ would appear.}~\label{fig:tail_packing}
  \end{figure}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{exp_rsection_fit.pdf}
  \caption{FWHM = 0.792 $\pm$ 0.009 $\AA^{-1}$}\label{fig:exp_rsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sim_rsection_fit.pdf}
  \caption{FWHM = 0.796 $\pm$ 0.011 $\AA^{-1}$}\label{fig:sim_rsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{exp_zsection_fit.pdf}
  \caption{FWHM = 0.110 $\pm$ 0.003 $\AA^{-1}$}\label{fig:exp_zsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sim_zsection_fit.pdf}
  \caption{FWHM = 0.163 $\pm$ 0.011 $\AA^{-1}$}\label{fig:sim_zsection_fit}
  \end{subfigure}
  \caption{
  The maximum intensity of R-$\pi$ generated from simulations of the ordered
  parallel displaced configuration is 3 times larger than experiment. The $q_r$
  cross-section of R-$\pi$ ((a) and (b)) is qualitatively different between 
  experiment (a) and simulation (b). We fit Lorentzian profiles to each peak and
  the FWHM (full width at half maximum) of the simulated pattern agrees with experiment within error. However
  the fit to the simulated data is affected by the three sharp peaks which appear
  near $q_r$ = 0. The $q_z$ cross-sections of R-$\pi$ ((c) and (d)) are 
  qualitatively similar. Each fits a Lorentzian profile well, however the FWHM
  of the simulated cross-section (d) is 48\% larger than the experimental 
  cross-section. Additionally, the peak of the simulated $q_z$ cross-section is 
  located at a lower $q_z$ value than experiment.}\label{fig:rpi_exp_comparison}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_sandwich.pdf}
  \caption{Sandwiched, Ordered Basin}\label{fig:z_correlation_sandwich}
  \end{subfigure}  
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_offset.pdf}
  \caption{Parallel Displaced, Ordered Basin}\label{fig:z_correlation_offset}
  \end{subfigure}  
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_sandwich_disordered.pdf}
  \caption{Sandwiched, Disordered Basin}\label{fig:z_correlation_sandwich_disordered}
  \end{subfigure}  
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_offset_disordered.pdf}
  \caption{Parallel Displaced, Disordered Basin}\label{fig:z_correlation_offset_disordered}
  \end{subfigure}  
  \caption{1D correlation functions of the center of masses of aromatic head
	  groups, $g(z)$, show decaying oscillatory behavior and have consistent correlation lengths with experiment. We calculated the
	  correlation length by fitting a decaying exponential function
	  (Equation~\ref{eqn:decaying_exponential}) to the peaks of $g(z)$. The
	  correlation length is longer for ordered basin systems
	  (Table~\ref{table:correlation_length}). We did not attempt to calculate the
	  correlation length for (d) because there are no clear peaks. We assume that its
	  correlation length is less than the vertical distance between monomers.}\label{fig:correlation}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{intensity_vs_zsigma.pdf}
  \caption{}\label{fig:intensity_vs_zsigma}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{rpi_xsection_vs_zsigma.pdf}
  \caption{}\label{fig:rpi_xsection_vs_zsigma}
  \end{subfigure}
  \caption{We can decrease the maximum intensity of R-$\pi$ by increasing
  thermal noise in the $z$-direction, however the $q_r$ cross-section profile does
  not change. (a) The intensity of R-$\pi$ drops precipitously as we increase
  $\sigma_z$. We can decrease the intensity of R-$\pi$, relative to the
  background intensity, relative to systems with simulation levels of disorder (blue)
  %as seen in simulation (blue) 
  by a factor of 3 when we
  increase $\sigma_z$ by 12\% (green) and by a factor of 15 when we increase
  $\sigma_z$ by 27\% (red). (b) Although the maximum intensity of R-$\pi$
  decreases with increasing $\sigma_z$, the peak shape remains the same.}\label{fig:znoise}
  \end{figure}

  However, when we allow monomer columns to move independently in the
  $z$-direction, the intensity of R-$\pi$ drops and the $q_r$ cross-section of
  the simulated diffraction patterns smooths out. We can demostrate this by
  creating a simplified sandwiched configuration (simplified in the same way as
  described above), 
  %simple systems 
  %MRS10: simple systems is not very exact. Point scatters that represent the head groups?
  %BJC11: It feels redundant and wordy saying the above rather than simple systems.
  with varying amounts of statistical correlation between columns. In the low
  limit, the COM of columns are situated at the same $z$-coordinate.
  We allow increasing independence of columns by randomly shifting each column in
  the $z$-direction according to a uniform distribution bounded by (0, $f \times
  \mathit{d}_{equil}$) where $f$ ranges between 0 and 1. We limit this discussion
  to the sandwiched configuration since it is not feasible for columns in the
  parallel displaced configuration, as we have set them up, to move past each
  other. When $f = 1$, the columns move independently and the $q_r$ cross-section
  smooths out completely (Figure~\ref{fig:column_displacement}). Any amount of
  dependence results in some presence of independent sharp peaks, though
  significantly attenuated at $f$ nearer 1. The intensity of R-$\pi$ also
  decreases with increasing column independence. We see an 8-fold decrease in the
  intensity of R-$\pi$ when $f=1$ versus when $f=0$ for our simplified model
  systems.

  % produce figures with: structure_factor.py --random_columns -nframes 1000 --hexagonal -g 86 86 256 -thermal_disorder 2.30 0.43 1.48 -dbwl 4.4 --pore_radius 6.6 -box 85 85 352 -sr 0
  % Adjust sr from 0 to .75 to 1
  \begin{figure}
  \centering
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_sr0.pdf}
  \caption{$f$ = 0}\label{fig:sf_qy_sr0}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_sr75.pdf}
  \caption{$f$ = 0.75}\label{fig:sf_qy_sr75}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_sr100.pdf}
  \caption{$f$ = 1}\label{fig:sf_qy_sr100}
  \end{subfigure}
  \caption{As we increase column independence using the $f$ parameter, the
	  intensity of R-$\pi$ decreases and the $q_r$ cross-section of the simulated
	  diffraction pattern becomes more smooth.  (a) When we place all columns at the
	  same reference $z$ coordinate, $f$ = 0, the intensity of R-$\pi$ is 18.3 and is
	  characterized by sharp Bragg-like peaks. (b) When columns have a moderate
	  amount of independence, $f$ = 0.75, the intensity of R-$\pi$ decreases 5-fold
	  to 3.7. The edges of the peak are beginning to smooth out, but sharp peaks
	  still exist. (c) When columns are completely independent, $f$ = 1, the
	  intensity of R-$\pi$ decreases 8-fold to 2.3 and the cross-section is
          relatively smooth.}\label{fig:column_displacement}
  \end{figure}

@@

  %BJC9: Note that the magnitude of the correlation function is much lower than 
  % in figure 10a. That's because many of the z-slices are zero when you include
  % all of them.
  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{z_correlation_fullbox.pdf}
  \caption{When we average all $z$-slices of the 3D correlation function, the 
  correlation length of the ordered sandwich configuration nearly triples.}\label{fig:z_correlation_fullbox}
  \end{figure}

@@

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{qy_fwhm.pdf}
  \caption{Increasing the amount of disorder in the $xy$ plane decreases the
	  FWHM of the $q_y$ cross-section of R-$\pi$. When we cut the amount of $r$ and
	  $\theta$ disorder in half (Noise factor = 0.5), the FWHM increases by 88\%. When
	  we double the disorder (Noise factor = 2), the FWHM decreases by
	  51\%.}\label{fig:qy_fwhm}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sandwiched_ensemble_rsection.pdf}
  \caption{Sandwiched}\label{fig:sandwiched_ensemble_rsection}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_rsection.pdf}
  \caption{Parallel Displaced}\label{fig:offset_ensemble_rsection}
  \end{subfigure}
  \caption{The $q_r$ section of R-$\pi$ is much smoother when we generate simulated XRD
  		   patterns from an ensemble of 40 independent simulations, suggesting that much of the extra initial intensity may be due to the starting conditions. The maximum 
  		   intensity of R-$\pi$ is 3$\times$ higher in the sandwiched configuration (a)
  		   than in the parallel displaced configuration (b).}\label{fig:ensemble_XRD}
  \end{figure}

@@

  %BJC15: will not waste much time formatting until we converge on a figure 
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_pooled.pdf}
  \caption{Distributions of deviations from ideal positions generated with data
  from all independent simulations}\label{fig:offset_ensemble_pooled}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  % BJC15: Also, do you have a preference for 1-sigma or 95 % confidence intervals? I think the 95 % is fine as is
  %MRS15: 95% is fine.
  \includegraphics[width=\textwidth]{offset_ecdfs.pdf}
  \caption{Empirical cumulative distribution functions generated from (a) and
  from simulation ensembles.}\label{fig:offset_ecdfs}
  \end{subfigure}
  \caption{(a) The distributions of the head group COM deviations
  from their idealized positions generated using pooled data from all
  frames of each independent configuration are symmetric, implying that 
  there is equal probability for a head group to displace in the positive
  or negative $z$, $r$ or $\theta$-direction. (b) The COM position of a 
  given head group is displaced randomly upon quenching. The ECDF generated from
  the pooled distributions (black) in (a) agree with the means of the 
  ECDFs generated from each COM (red). The red error bars are larger than
  the black error bars since there is a wider distribution of mean COM
  deviations than the mean deviations of distributions sampled from the full
  distribution.}\label{fig:full_ensemble_distributions}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_stds.pdf}
  \caption{}\label{fig:offset_ensemble_stds}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_means.pdf}
  \caption{}\label{fig:offset_ensemble_means}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_regional_density.pdf}
  \caption{}\label{fig:offset_ensemble_regional_density}
  \end{subfigure}
  \caption{(a) The standard deviation of the distribution of quenched disorder
  from the first 5 ns of the main ordered parallel displaced system studied in
  this paper (black dashed line) is in agreement with the distribution of quenched disorder 
  standard deviations calculated from the ensemble of simulations (histogram). 
  (b) The mean values of $r$ and $\theta$ from the first 5 ns of the main
  system trajectory (black dashed line) is in agreement with the distribution of mean values
  calculated from each simulation in the ensemble (histogram). The mean values of $z$
  are necessarily 0 so they are not plotted. (c) The radial densities of tail
  atoms, head group atoms and sodium atoms calculated from the first 5 ns of the
  main system simulation trajectory (black lines) and from the ensemble of 
  trajectories (all other lines) look qualitatively similar.}\label{fig:ensemble_stds}
  \end{figure}
